---
title: "Results Exploratory Analysis"
author: "Luis Mesias"
date: "11/9/2021"
output:
  html_document: 
    code_folding: hide
    number_sections: TRUE
    toc_float: TRUE
    toc: TRUE
    df_print: paged
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

# Setup
## Importing

```{r, message = FALSE, warning = FALSE}
library(broom);
#library(equatiomatic); old version
library(ggrepel);
library(janitor);
library(knitr);
library(magrittr);
library(naniar);
library(patchwork);
#library(rstanarm);old version
library(tidyverse);
library(forecast)
library("readxl");
library(ggforce);
library(FSA);
library(ggsignif);
theme_set(theme_bw())
std.error <- function(x) sd(x)/sqrt(length(x))
```

## Reading Data

Read the data from the three different sections: basic subject data, threshold data, and sensory perception data. 
```{r}
usefulData <- read_excel("explodata.xlsx", sheet=1) %>%
  clean_names()%>% 
  mutate(combination = factor(combination));
electrodeData <- read_excel("explodata.xlsx", sheet=2) %>%
  clean_names()%>% 
  mutate(electrode = factor(electrode), subject = factor(subject));
combinationData <- read_excel("explodata.xlsx", sheet=3) %>%
  clean_names()%>% 
  mutate(combination = factor(combination), subject = factor(subject));
polarityData <- read_excel("explodata.xlsx", sheet=4) %>%
  clean_names()%>% 
  mutate(pulse = factor(pulse), subject = factor(subject), combination = factor(combination));
polarityData2 <- read_excel("explodata.xlsx", sheet=6) %>%
  clean_names()%>% 
  mutate(pulse = factor(pulse), subject = factor(subject), combination = factor(combination));
statsIntensityData <- read_excel("explodata.xlsx", sheet=8) %>%
  clean_names()%>% 
  mutate(metric = factor(metric), stimulation_instensity = factor(stimulation_instensity));
```

## Data
```{r}
polarityData
```

## Plot
Electrode Distance
```{r}
usefulData %>%
    ggplot(data = usefulData, mapping = aes(x=inter_electrode_distance, y=useful_ratio, color = factor(combination, levels =c('Finger-Finger', 'Palm-Palm', 'Finger-Palm'))), position =position_dodge(width=1), size =2) +
    geom_point(size = 4, alpha = 1/2)+
    geom_smooth(method="lm", se=F)+
  labs(title = "Useful Ratio with Increasing Inter-Electrode Distance per \n Electrode Combination Type",
         y = "Useful Ratio (Useful/Total)",
         x = "Inter-Electrode Distance (Sections)") +
    scale_color_manual(name="Legend",
        breaks=c("Finger-Finger", "Palm-Palm", "Finger-Palm"),
        values = c("Finger-Finger" = "#349beb", "Palm-Palm"="#eb34c3", "Finger-Palm"="#eba534"))+
    theme(legend.position="bottom")
ggsave("explo_res.jpg")
```

Electrodes
```{r}
electrodeData.sum <- electrodeData %>%
  group_by(electrode) %>%
  summarise( 
    n=n(),
    mean=mean(percentage),
    sd=sd(percentage)
  )
electrodeData.sum %>%
    ggplot(data = electrodeData.sum, mapping = aes(x=reorder(electrode, -mean), y=mean)) +
    geom_bar(stat='identity', fill = "#349beb")+
    geom_errorbar(mapping =aes(ymin=mean-sd, ymax=mean+sd), width =0.3)+
  labs(title = "Percentage of Useful Trials per Total Trials for Each Electrode Position",
         y = "Useful Average Percentage (%)",
         x = "Electrode Postion")+
  theme(axis.text = element_text(size = 11))   
ggsave("explo_res_elec.jpg")
```

Combinations
```{r}
combinationData.sum <- combinationData %>%
  group_by(combination) %>%
  summarise( 
    n=n(),
    mean=mean(percentage),
    sd=sd(percentage)
  )
combinationData.sum %>%
    ggplot(data = combinationData.sum, mapping = aes(x=reorder(combination, -mean), y=mean)) +
    geom_bar(stat='identity', fill = "#349beb")+
    geom_errorbar(mapping =aes(ymin=mean-sd, ymax=mean+sd), width =0.3)+
    labs(title = "Percentage of Useful Trials per Total Trials for Each Electrode Combination",
         y = "Useful Average Percentage (%)",
         x = "Electrode Combination")+
  theme(axis.text = element_text(size = 11))
ggsave("explo_res_combination.jpg")
```

Polarity
```{r}
polarityData.sum <- polarityData %>%
  group_by(combination, pulse) %>%
  summarise( 
    n=n(),
    mean=mean(percentage),
    sd=sd(percentage),
    combination=combination,
    pulse=pulse
  )
```

Normality test polarity
```{r}
p1 <- ggplot(polarityData, aes(x = percentage)) +
    geom_histogram(fill = "slateblue", col = "white", 
                   binwidth = 1) + 
    labs(x = "percentage") +
    theme_bw()

p2 <- ggplot(polarityData, aes(sample = percentage)) +
    geom_qq(col = "slateblue") + geom_qq_line(col = "red") + 
    labs(y = "percentage") +
    theme_bw()

p3 <- ggplot(polarityData, aes(x = "", y = percentage)) +
    geom_violin() + 
    geom_boxplot(fill = "slateblue", width = 0.3, notch = TRUE) + 
    labs(y = "percentage",
         x = "") +
    theme_bw() + 
    coord_flip()

p1 + p2 - p3 +
  plot_layout(ncol = 1, height = c(3, 2))
```
data is not normally distributed

performing a Kruskal-Wallis test to check that polairty independence is statistically significant 

```{r}
polarityData.f <- polarityData2 %>%
  group_by(pulse) %>%
  summarise(
    count = n(),
    mean = mean(useful_for_polarity, na.rm = TRUE),
    sd = sd(useful_for_polarity, na.rm = TRUE),
    median = median(useful_for_polarity, na.rm = TRUE),
    useful_for_polarity= useful_for_polarity
  )

polarityData.f

kruskal.test(useful_for_polarity ~ pulse, data = polarityData.f)

dunnTest(useful_for_polarity ~ pulse, data=polarityData.f,method="bonferroni")
```

performing a Kruskal-Wallis test to check that polairty independence is statistically significant by group

```{r}
polarityData.f <- polarityData %>%
  group_by(pulse) %>%
  summarise(
    count = n(),
    mean = mean(useful_for_polarity, na.rm = TRUE),
    sd = sd(useful_for_polarity, na.rm = TRUE),
    median = median(useful_for_polarity, na.rm = TRUE),
    useful_for_polarity= useful_for_polarity
  )

polarityData.f

kruskal.test(useful_for_polarity ~ pulse, data = polarityData.f)

dunnTest(useful_for_polarity ~ pulse, data=polarityData.f,method="bonferroni")
```


```{r}
polarityData.sum %>%
    ggplot(data = polarityData.sum, mapping = aes(x=combination, y=mean, fill = factor(pulse, levels =c('Anodic', 'Cathodic', 'Neither(Same area)', 'Useful')))) +
    geom_bar(stat='identity',position = position_dodge(width=0.9))+
    geom_errorbar(mapping =aes(ymin=mean-sd, ymax=mean+sd),position = position_dodge(width=0.9), width =0.3)+
  labs(title = "Polarity Dependent (PD) and Indepndent (PI) Trials per Electrode Combination",
         y = "Average Percentage of Trials With Useful Percepts (%)",
         x = "Electrode Combination")+
  scale_fill_manual(name="",
        breaks=c("Anodic", "Cathodic" , "Neither(Same area)", "Useful"),
        values = c("Anodic" = "#349beb", "Cathodic"="#eb34c3", "Neither(Same area)"="#eba534", "Useful"="#32b347"),
        labels=c("PD Cathodic Pulse on\nMore Distal Electrode", "PD Cathodic Pulse on\nMore Proximal Electrode" , "PD Cathode/Anode on Same\nPhalange or Palm Region", "PI Useful\nTrials"))+
  theme(legend.position="bottom",axis.text = element_text(size = 11))
ggsave("explo_res_polarityComb.jpg")

polarityDataSub.sum <- polarityData %>%
  group_by(subject, pulse) %>%
  summarise( 
    n=n(),
    mean=mean(percentage),
    sd=sd(percentage),
    subject=subject,
    pulse=pulse
  )

polarityDataSub.sum %>%
    ggplot(data = polarityDataSub.sum, mapping = aes(x=subject, y=mean, fill = factor(pulse, levels =c('Anodic', 'Cathodic', 'Neither(Same area)', 'Useful')))) +
    geom_bar(stat='identity',position = position_dodge(width=0.9))+
    geom_errorbar(mapping =aes(ymin=mean-sd, ymax=mean+sd),position = position_dodge(width=0.9), width =0.3)+
  labs(title = "Polarity Dependent (PD) and Indepndent (PI) Trials for Each Participant",
         y = "Average Percentage of Trials With Useful Percepts (%)",
         x = "Participants")+
  scale_fill_manual(name="",
        breaks=c("Anodic", "Cathodic" , "Neither(Same area)", "Useful"),
        values = c("Anodic" = "#349beb", "Cathodic"="#eb34c3", "Neither(Same area)"="#eba534", "Useful"="#32b347"),
        labels=c("PD Cathodic Pulse on\nMore Distal Electrode", "PD Cathodic Pulse on\nMore Proximal Electrode" , "PD Cathode/Anode on Same\nPhalange or Palm Region", "PI Useful\nTrials"))+
  theme(legend.position="bottom",axis.text = element_text(size = 11))
ggsave("explo_res_polaritySub.jpg")
```

stats data plot

```{r}
statsIntensityData %>%
    ggplot(data = statsIntensityData, mapping = aes(x=metric, y=mean, fill = factor(stimulation_instensity, levels =c('Perception Threshold', 'Maximum Comfortable')))) +
    geom_point(data = statsIntensityData, position =position_dodge(width=0.5), size = 3, mapping = aes(x=metric, y=mean, color = factor(stimulation_instensity, levels =c('Perception Threshold', 'Maximum Comfortable'))))+
      geom_errorbar(mapping =aes(ymin=mean-sd, ymax=mean+sd, color = factor(stimulation_instensity, levels =c('Perception Threshold', 'Maximum Comfortable'))), width =0.4, position =position_dodge(width=0.5))+
  geom_signif(xmin=c(0.875, 1.875, 2.875), xmax=c(1.125, 2.125, 3.125),
                              y_position=c(3, 3.75, 2), annotation=c("***", "***","*")) +
    labs(title = "The Effects of Stimulation Intensity Across All Electrodes and Participants",
         y = "Sensation Location (Phalanges)",
         x = "Metric") +
      ylim(-0.5,4)+
    scale_fill_manual(name="Pulse Width",
        breaks=c("Perception Threshold", "Maximum Comfortable"),
        values = c("Perception Threshold" = "#4C46FF", "Maximum Comfortable"="#FF3939"))+
      scale_color_manual(name="Pulse Width",
        breaks=c("Perception Threshold", "Maximum Comfortable", "Active Electrode"),
        values = c("Perception Threshold" = "#4C46FF", "Maximum Comfortable"="#FF3939"))+
  guides(fill = guide_legend(override.aes = list(shape = 21)), shape = "none")+
      theme(legend.position = "bottom")
  
  ggsave("Stats_All_Envelopes.jpg")
```


